Improved fluid phantom for accurate relative flow calculations for speckle contrast imaging

### 2022-02-01 article.tex
Incorporate Andy text edits

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{blindtext}

@@

Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify the visualization of controlled flow changes in modified systems. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged. For applications in rodent studies, 1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}. This speed is converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are commonly believed to provide a highly-controlled flow output. A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.

@@

In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regularized flow system. By understanding the associated uncertainty with each system, we can provide insight on the experimental design for a microfluidic study that aims to assess the hardware performance of an optical system, without fear that performance can be compromised due to flow-related noise. Quantifying this error allows us to accurately determine the true sensitivity to relative flow changes of a MESI system. Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%. The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.

The remainder of the paper can be summarized as follows: Section \ref{sect:methods} describes the microfluidic phantom fabrication and the different experimental tests to assess the uncertainty with the syringe pump and pressure regulated systems, the instrumentation for the MESI system, and the mathematical formulation necessary to calculate relative flow from the data collected with the MESI system. Results from these experimental protocols, namely the uncertainty analysis and the MESI flow calculations, are presented in Section \ref{sect:results}. Lastly, the paper findings and contributions are summarized in Section \ref{sect:discussion}.

@@

The uncertainty in repeatability, which is a measure of within-run variance, was defined as:
%
% Equation 1 - Uncertainty in Repeatability
\begin{equation}
    \label{eq:u_repeat}
    u_\textnormal{repeat} = 100 \times \frac{s_p}{\bar{x}}
\end{equation}

@@

The uncertainty in reproducibility, which is a measure of between-run variance, was defined as:
%
% Equation 2 - Uncertainty in Reproducibility
\begin{equation}
    \label{eq:u_reproduce}
    u_\textnormal{reproduce} = 100 \times \frac{s}{\bar{x}}
\end{equation}

@@

Finally, the uncertainty in measurement bias, was defined as:
%
% Equation 3 - Uncertainty in Bias
\begin{equation}
    \label{eq:u_bias}
    u_\textnormal{bias} = 100 \times \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
\end{equation}

>>>>

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}
\usepackage{blindtext}
\usepackage{xcolor}

@@

Due to its wide adoption, LSCI instrument design and development is an active area of research, and microfluidic studies are commonly used to quantify controlled flow changes in well-defined channels. Typically, studies designed to mimic blood flow involve the use of a flow channel embedded in a polydimethylsiloxane (PDMS) background \cite{Parthasarathy:2008el}, glass capillary tubing \cite{Choi:2004jn}, or clear plastic tubing \cite{Miao:2014}. More complex microfluidic networks have also been fabricated in glass, plastic, and epoxy substrates to represent superficial heterogenous vasculature \cite{Luu.2012}. A scattering solution \cite{Parthasarathy:2008el} or whole blood\cite{Choi:2004jn,Miao:2014} is then flowed through the channel at controlled rates and imaged. For applications in rodent studies, 0.1 -- 10 mm/s is a commonly selected range of speeds, since this corresponds to the capillary speeds measured in rodents \cite{Tomita:2008do}. This speed is converted to a flow rate using the cross-sectional area of the flow channel, which is used to program the flow control system.

Syringe pumps are the most widely used flow control system in microfluidic studies and are commonly believed to provide a highly-controlled flow output. \textcolor{red}{A review on the subject in 2016 \cite{Richards.2015} found that in the LSCI community, all published microfluidic studies ($>$20) used syringe pumps}; this trend has continued to this date with more recent papers continuing to use syringe pump systems for flow control \cite{Zheng:2018ct,Yang.2019}. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and take a longer time to achieve desired flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult to obtain both stable flow and fast flow response with a syringe pump flow control system.

@@

In this paper, we address two primary objectives: first, we quantify the uncertainty associated with both a syringe pump and a pressure regulated flow system. By understanding the associated uncertainty with each system, we can provide insight on the experimental design for a microfluidic study that aims to assess the hardware performance of an optical system, without fear that performance can be compromised due to flow-related noise. Quantifying this error allows us to accurately determine the true sensitivity to relative flow changes of a MESI system. \textcolor{red}{Secondly, we demonstrate that a MESI system can resolve very small changes in relative flow, as small as 2\%.} The ability for MESI to resolve such small changes in relative flow, which are smaller than the combined uncertainty of the syringe pump system, indicate that to properly assess the performance of novel hardware for a LSCI or MESI system, a pressure-driven flow system should be used.

@@

The uncertainty in repeatability, which is a measure of within-run variance, was defined as:
%
% Equation 1 - Uncertainty in Repeatability
\begin{equation}
    \label{eq:u_repeat}
    u_\textnormal{repeat} = 100\left(\frac{s_p}{\bar{x}}\right)
\end{equation}

@@

The uncertainty in reproducibility, which is a measure of between-run variance, was defined as:
%
% Equation 2 - Uncertainty in Reproducibility
\begin{equation}
    \label{eq:u_reproduce}
    u_\textnormal{reproduce} = 100\left(\frac{s}{\bar{x}}\right)
\end{equation}

@@

Finally, the uncertainty in measurement bias, was defined as:
%
% Equation 3 - Uncertainty in Bias
\begin{equation}
    \label{eq:u_bias}
    u_\textnormal{bias} = 100 \left| \frac{\bar{x} - x_{ref}}{x_{ref}} \right|
\end{equation}
